\thispagestyle{plain}
 \vspace{.03cm}
 \noindent
 \begin{table}
 \centering
 \begin{tabular}{p{3.75in}p{3in}}
  & \Letter \hspace{2pt} \href{mailto:shakyas@appstate.edu}{shakyas@appstate.edu} \\
 & \Mundus \hspace{2pt} \href{https://shishirshakya.github.io}{https://shishirshakya.github.io} \\
 & \Mundus \hspace{2pt} \href{https://scholar.google.com/citations?user=mvYtqK8AAAAJ&hl=en}{Google Scholar}\\
 & \Mundus \hspace{2pt} \href{https://orcid.org/0000-0002-6272-6654}{ORCID: 0000-0002-6272-6654}\\
 & \Smiley \hspace{2pt} \textbf{Citizenship: U.S. Citizen} \\
 \end{tabular} 
 \end{table} \vspace*{-10mm}

\section*{RESEARCH INTERESTS}
\begin{list1}
\itemsep0em
\item[] Applied Econometrics and Causal Inference, Health Economics, Healthcare Workforce and Regulation, Opioid Crisis and Substance Use, Public Choice and Regulatory Economics, Institutional Economics
\end{list1}

\section*{TECHNICAL EXPERTISE}
\begin{list1}
\itemsep0em
\item[] Programming and data analysis: R, SQL, Python, \LaTeX
\item[] OMOP Common Data Model (CDM) and clinical care analytics
\item[] Development and deployment of locally hosted Agentic-AI systems for research
%\item[] Ed-tech platform development: Founding Engineer of \href{https://mymeritguide.com/}{MyMeritGuide}, a FERPA compliant agentic AI-powered assessment platform for scalable oral examinations and authentic student learning validation
\end{list1}

\section*{EDUCATION}
\begin{list1}
\itemsep0em
\item[] \textbf{Ph.D. in Economics}: West Virginia University, United States \hfill 2016-2020
% \item[] \textbf{M.A. in Economics}: West Virginia University, United States, \hfill 2016-2019
\item[] \textbf{M.A. in Economics}: Tribhuvan University, Nepal \hfill 2011-2013
\item[] \textbf{B.A. in Economics}: Tribhuvan University, Nepal \hfill 2006-2009
\end{list1}

\section*{ACADEMIC POSITIONS AND TEACHING}
\begin{list1}
\itemsep0em
\item[] \textbf{Assistant Professor of Economics}: \textit{Appalachian State University} \hfill Aug 2023-Current
\begin{list1}
\itemsep0em
\item[] Applied Econometrics \hfill Spring 2026, Fall 2025
\item[] Principles of Microeconomics \hfill Fall 2024
\item[] Forecasting and Time Series Models \hfill Spring 2025/24, Fall 2023
\item[] Forecasting and Time Series Models (MBA) \hfill Spring 2024
\item[] Business and Economic Statistics II \hfill Spring 2025/26, Fall 2025/24/23, Summer 2025/24
\end{list1}
\item[] \textbf{Assistant Professor of Economics}: \textit{Shippensburg University} \hfill Aug 2020-Jul 2023
\begin{list1}
\itemsep0em
\item[] Economic Analysis of Big Data, Regional Economics, Managerial Economics, Portfolio Optimization, Data Analytics, Principles of Macroeconomics, Principles of Microeconomics, Principles of Economics 
\end{list1}
\item[] \textbf{Graduate Teaching Assistant}: West Virginia University \hfill 2018-2020
\begin{list1}
\itemsep0em 
\item[] Elementary Business and Economic Statistics 
\item[] Principles of Macroeconomics 
\end{list1}
\item[] \textbf{Graduate Research Assistant}: Regional Research Institute (RRI), WVU \hfill 2016-2018
\item[] \textbf{Economic Consultant}: National Planning Commission, Nepal \hfill 2016
\end{list1}

\section*{RESEARCH AFFILIATIONS}
\begin{list1}
\itemsep0em
\item[] \textbf{Research Fellow}: \textit{Archbridge Institute} \hfill Jul 2025-Current
\item[] \textbf{Mentor}: \textit{AIM-AHEAD Bridge2AI AI-READI Funded by National Institutes of Health (NIH)} \hfill Feb 2026-Current
\item[] \textbf{Mentor}: \textit{AIM-AHEAD Clinicians Leading Ingenuity IN Al Quality (CLINAQ) Fellowship Funded by National Institutes of Health (NIH)} \hfill Jan 2026-Current

\item[] \textbf{Research Fellow}: \textit{AIM-AHEAD Bridge2AI for Clinical Care Training Program Funded by National Institutes of Health (NIH)} \hfill Jan 2025-Dec 2025
\item[] \textbf{Research Affiliate}: \textit{Knee Regulatory Research Center} \hfill Jul 2023-Current
\item[] \textbf{Visiting Research Fellow}: \textit{West Virginia University} \hfill Apr 2023-Jul 2023
\begin{list1}
\itemsep0em
\item[] Knee Regulatory Research Center at John Chambers College of Business and Economics 
\end{list1}
\end{list1}

\section*{CURRENT PROJECTS}
\begin{enumerate}
\item Thakkar, S. \& \textbf{Shakya, S.} (n.d.). The Economic Costs of Disaster-Related Property Damage: Valuing Mental Health Impacts of Climate Change.
\item Kanimian, S. \& \textbf{Shakya, S.} (n.d.). Ripple Effects by Ownership Types: Impact of Hospital Closures on Charges and Profitability.
\item Beniwal, S., \textbf{Shakya, S.}, Kanimian, S., \& Anderson, D. (n.d.). Impact of ACA Medicaid expansion on appointment wait time in community medical centers.
\item \textbf{Shakya, S.}, Ammons, J., and Geloso, V. (n.d.). The polyarchy paradigm: Unraveling corruption and fostering transparency.
\item Muhammad, N., \& \textbf{Shakya, S.} (n.d.). Hospital mergers and acquisitions: A financial profit analysis.
\item \textbf{Shakya, S.}, \& Jahan, I. (n.d.). Democracy and Women's Empowerment: Political Access vs. Economic Opportunity.
\item \textbf{Shakya, S.} \& Ammons, J. (n.d.). Impact of Recreational Marijuana Laws on Risky Behaviors.
\item Adhikari, M., \textbf{Shakya, S.}, Sylvia, S., \& Holmes, M. (n.d.). Cultural practices, gender norms, and household resource allocation in crisis.
\item \textbf{Shakya, S.}, \& Dutta, N. (n.d.). Financial inclusion for females and individualism: Does education act as a mediator?
\item \textbf{Shakya, S.}, \& Ghosh, S. (n.d.). Foreign Professional Credentialing: Addressing Labor Shortages by Tapping Underutilized Workforce.
\end{enumerate}

\section*{REVISE AND RESUBMIT}
\begin{etaremune}
\item \textbf{Shakya, S.}, \& Roy, A. (n.d.). Access to mental health care services and suicide rates in the United States. \textit{Journal of Policy Analysis and Management}.
\item Bailey, J., \& \textbf{Shakya, S.} (n.d.). The impact of repealing Certificate-of-Need laws on healthcare spending: A causal analysis. \textit{Health Economics}.
\item \textbf{Shakya, S.} and Ammons, J. (n.d.). The deep roots of revolution: Folklore and revolts. \textit{Journal of Public Finance and Public Choice}.
\item Ammons, J., Shakya, G., \& \textbf{Shakya, S.} (n.d.). Town, Gown, and Touchdowns: How Athletic Reclassification Shapes Local Entrepreneurial Ecosystems. \textit{Journal of Business Venturing Insights}.
\item \textbf{Shakya, S.}, Ammons, J., \& Mahmood, T. (n.d.). The Development Costs of Revolution: Evidence from Violent and Nonviolent Transitions. \textit{Kyklos}.
\end{etaremune}

\section*{UNDER REVIEW}
\begin{etaremune}
\item \textbf{Shakya, S.} \& Ammons, J. (n.d.). Legislative party cohesion and institutional checks and balances: Cross-country evidence, 1950--2024. \textit{Journal of Comparative Economics}.
\item Babaei-Balderlou, S. and \textbf{Shakya, S.} (n.d.). The Invisible Hand of Gen-AI: Can AI-Enhanced Study Groups Improve Learning Outcomes? \textit{The Journal of Economic Education}.
\item \textbf{Shakya, S.}, Bedi, J., and Plemmons, A. (n.d.). Scrubbed Down: Nurse Practitioner Scope of Practice and Entrepreneurship in the United States. \textit{Journal of Business Venturing}.
\item Sugg, M., Ulrich, S., Runkle, J., and \textbf{Shakya, S.} (n.d.). Geographic Access to Maternity Care and the Hidden Burden of Maternal Mental Health: A Spatial Analysis of Diagnosis Disparities in North Carolina. \textit{Obstetrics \& Gynecology}.
\item Deyo, D., \textbf{Shakya, S.}, Ampaabeng, K., Norris, C., \& Timmons, E. (n.d.). Unintended endings: The effects of municipal massage therapist licensing on crime. \textit{Southern Economic Journal}.
\item Bedi, J., \textbf{Shakya, S.}, \& Jia, S. (n.d.). Closing time: Impacts of deportation on entrepreneurship. \textit{Journal of Labor Research}. %\textit{Economics Letters}.
\item \textbf{Shakya, S.}, \& Nepal, T. (n.d.). More Access, Same Workforce: Evidence from the Physical Therapy Compact. \textit{Journal of Regulatory Economics}.
\item \textbf{Shakya, S.}, Morgan, A., Orozco, E., \& Timmons, E. (n.d.). Healthcare Policy Spillovers: Impact on Nurse Practitioners and Health Outcomes in North Carolina. \textit{Journal of Regulatory Economics}. \hfill \href{https://ssrn.com/abstract=6064866}{Download}

\end{etaremune}

\section*{PUBLICATIONS}
\begin{etaremune}
\item Miske, O., ...,  \textbf{Shakya, S.}, ... et al. (2026). Investigating the reproducibility of the social and behavioural sciences. \textit{Nature} \hfill \href{https://repository.essex.ac.uk/42891/1/SCOREreproducibility.fullmanuscript.pdf}{Download}

\item Tyner, A., ...,  \textbf{Shakya, S.}, ... et al. (2026). Investigating the replicability of the social and behavioural sciences. \textit{Nature} \hfill \href{https://osf.io/preprints/metaarxiv/b7x8f}{Download}

\item Ammons, J., \textbf{Shakya, S.} \& Zhukov, K. (2026). Covert Regime Change and Ideology. \textit{Public Choice}. \hfill \href{https://link.springer.com/article/10.1007/s11127-026-01382-w}{Download}


\item \textbf{Shakya, S.} and Ammons, J. (2025). The Invisible Hand Meets the Raised Fist: Social Movements and Market Legitimacy. \textit{Journal of Economic Behavior \& Organization}. \hfill \href{https://www.dropbox.com/scl/fi/gqvbgmgf2midszre44cyf/The-Invisible-Hand-Meets-the-Raised-Fist.pdf?rlkey=fg7jdpiv4w9xlw5tgoyl66j4s&st=0bttotm2&dl=0}{Download}


\item Ammons, J., \textbf{Shakya, S.}, \& Callais, J. T. (2025). What do women get from a successful revolution? \textit{Journal of Institutional Economics}. \hfill \href{https://www.dropbox.com/scl/fi/691ysf6zimszgb1b3wscz/what-do-women-get-from-a-successful-revolution.pdf?rlkey=1yebirjrvyaq7yl2jt8mdf0ob&st=5rhg36b8&dl=0}{Download}

\item Hodges, C. \& \textbf{Shakya, S.} (2025). Prescription opioid spillovers: Retail pharmacies level analysis. \textit{Journal of Substance Use and Addiction Treatment}. \hfill \href{https://www.dropbox.com/scl/fi/sto4f3852u4mbzur56ih1/Prescription-opioid-spillovers_-Retail-pharmacy-level-analysis.pdf?rlkey=mb52o2583pgs17660hkd7d5ke&st=afw12tku&dl=0}{Download}

\item Nepal, T., \& \textbf{Shakya, S.} (2025). Scope-of-practice regulations and physician assistant inter-state mobility. \textit{Journal of Labor Research}. \hfill \href{https://www.dropbox.com/scl/fi/tqgnrk9fxrvznrlokdhmk/Shakya-Scope-of-Practice-Regulations-and-Physician-Assistant-Inter-State-Practice-Relocation.pdf?rlkey=usoy1gpnm952ocwktug0tcoac&st=ahe0oxz0&dl=0}{Download}

\item Sugg, M., \textbf{Shakya, S.}, Ulrich, S., Runkle, J., \& Tyson, J. (2025). Mapping maternity care deserts: Driving distance and health outcomes in North Carolina. \textit{The Journal of Rural Health}. DOI: 10.1111/jrh.70020. (NRHA Article of the Year, 2026.) \hfill \href{https://www.dropbox.com/scl/fi/6vupzn4iwu2jzzl4gnhtc/The-Journal-of-Rural-Health-2025-Sugg-Mapping-maternity-care-deserts-Driving-distance-and-health-outcomes-in-North.pdf?rlkey=zia9y7p4vinyz5uc72q0lzuct&st=g5om58hn&dl=0}{Download}

\item \textbf{Shakya, S.}, Nepal, T., Mathew, M., \& Timmons, E. (2024). Anti-maintenance of certification and elderly physician supply. \textit{Economics Letters}. \hfill \href{https://www.dropbox.com/scl/fi/fqb0916bkwk97m4we1riz/Anti-maintenance-of-certification-and-elderly-physician-supply.pdf?rlkey=2qqz14u2x47qfjy7ravd7d0o7&st=r1x2agmo&dl=0}{Download}

\item \textbf{Shakya, S.}, \& Plemmons, A. (2024). Scope of practice and opioid prescribing behavior of nurse practitioners serving Medicare beneficiaries. \textit{Health Economics}. \hfill \href{https://www.dropbox.com/scl/fi/wfmbm1mc9hqyzhkqp9rxh/Shakya-Plemmons-HE-2024.pdf?rlkey=nlb07mwl20nsox976xla7inhg&st=kp9of3qz&dl=0}{Download}

\item Scarcioffolo, A., Mugabe, D., \& \textbf{Shakya, S.} (2024). Stuck in the middle: The conundrum of firms' responsiveness to environmental policy in shale production. \textit{Applied Economics Letters}. \hfill \href{https://www.dropbox.com/scl/fi/w5kh21t0f5q2uiqjpei98/Stuck-in-the-middle-the-conundrum-of-firms-responsiveness-to-environmental-policy-in-shale-production.pdf?rlkey=j0hb5mevqm08lm11dp9zjscdn&dl=0}{Download}

\item \textbf{Shakya, S.}, Plemmons, A., \& Norris, C. (2024). Military spouse licensing: A case study of registered nurses near military bases. \textit{Journal of Regulatory Economics}. \hfill \href{https://link.springer.com/article/10.1007/s11149-024-09480-7}{Download}

\item Beniwal, S., \& \textbf{Shakya, S.} (2024). Hospital ownership changes and charge-to-cost shifts. \textit{Economics Letters}. \hfill \href{https://www.dropbox.com/scl/fi/nob6hng0eydoob8ja7d1h/HospitalOwnershipChangeAndCostAnalysis.pdf?rlkey=2qaufyd6evfcatbbtmcwxnex8&dl=0}{Download}

\item Ammons, J., \& \textbf{Shakya, S.} (2024). Revolutions and corruption. \textit{Public Choice}. \hfill \href{https://link.springer.com/article/10.1007/s11127-024-01173-1}{Download}

\item \textbf{Shakya, S.}, \& Bretschneider Fries, C. (2024). The effect of substance use Certificate-of-Need laws on access to substance use disorder treatment facilities. \textit{Southern Economic Journal}. \hfill \href{https://www.dropbox.com/scl/fi/fkhpvcf0ico3xjxjcs66b/Southern-Economic-Journal-2024-Shakya-The-effect-of-substance-use-Certificate-of-Need-laws-on-access-to-substance-use.pdf?rlkey=lapu9zmq0x9gwe362ttpeailb&dl=0}{Download}

\item \textbf{Shakya, S.}, Plemmons, A., Bae, K., \& Timmons, E. (2024). The pharmacist will see you now: Pharmacist prescriptive authority and access to care in Idaho. \textit{Contemporary Economic Policy}. \hfill \href{https://onlinelibrary.wiley.com/doi/full/10.1111/coep.12647}{Download}

\item \textbf{Shakya, S.}, \& Levinstein, M. (2024). Grading policy, email nudges, and grade outcomes. \textit{The Journal of Economic Education}. \hfill \href{https://www.dropbox.com/scl/fi/o9seuixtlkn74xdnzljcw/Grading-policy-email-nudges-and-grade-outcomes.pdf?rlkey=i1k0jzv8h55txa5625x35ik1g&dl=0}{Download}

\item Shah Mobariz, A., \& \textbf{Shakya, S.} (2024). Cultural influences on gender gap in test scores: Findings from Afghanistan's university entrance examination. \textit{Applied Economics Letters}. \hfill \href{https://www.tandfonline.com/doi/pdf/10.1080/13504851.2024.2332523}{Download}

\item Bae, K., Norris, C., \textbf{Shakya, S.}, \& Timmons, E. (2023). Advanced practice registered nurse full practice authority, provider supply, and health outcomes: A border analysis. \textit{Policy, Politics, and Nursing Practice}. \hfill \href{https://www.dropbox.com/scl/fi/4vw2vcl9v5ckwrmnjloxk/Advanced-Practice-Registered-Nurse-Full-Practice-Authority-Border-Analysis.pdf?rlkey=c11r6bonquwwn2elijdnxjtgb&dl=0}{Download}

\item Neto, A., Nowicki, J., \& \textbf{Shakya, S.} (2023). Do public libraries help mitigate crime? Evidence from Kansas City, MO. \textit{The Journal of Cultural Economics}. \hfill \href{https://www.dropbox.com/scl/fi/17fe6rp5xi12xcgkkq34i/Do-Public-Libraries.pdf?rlkey=kg5bzwtp370i2n77gcdhrxorq&dl=0}{Download}

\item \textbf{Shakya, S.}, \& Ruseski, J. (2023). The effect of prescription drug monitoring programs on county-level opioid prescribing practices and spillovers. \textit{Contemporary Economic Policy}. \hfill \href{https://www.dropbox.com/scl/fi/uwjo6pk4fvri714j9vgzc/Contemporary-Economic-Policy-2023-Shakya-The-effect-of-Prescription-Drug-Monitoring-Programs-on-county-level-opioid.pdf?rlkey=het575mm5mdsgi53gyljbjzok&dl=0}{Download}

\item Plemmons, A., \textbf{Shakya, S.}, Cato, K., Sadarangani, T., Poghosyan, L., \& Timmons, E. (2022). Exploring the relationship between nurse practitioner full practice authority, nurse practitioner workforce diversity, and disparate primary care access. \textit{Policy, Politics, and Nursing Practice}. \hfill \href{https://www.dropbox.com/scl/fi/vtfnitm93hofjjdzg95yi/Exploring-the-Relationship-between-Nurse-Practitioner-Full-Practice-Authority-Nurse-Practitioner-Workforce-Diversity-and-Disparate-Primary-Care-Access.pdf?rlkey=716aejw18by42z96qx1qoq3sd&dl=0}{Download}

\item \textbf{Shakya, S.}, \& Hodges, C. (2022). Must access prescription drug monitoring programs and retail opioid sales. \textit{Contemporary Economic Policy}. \hfill \href{https://www.dropbox.com/scl/fi/d2yash55gkz0j8wvkn61o/Contemporary-Economic-Policy-2022-Shakya-Must-access-prescription-drug-monitoring-programs-and-retail-opioid-sales.pdf?rlkey=zno0w3llwq2i5kz1ioivdrogo&dl=0}{Download}

\item \textbf{Shakya, S.}, Ghosh, S., \& Norris, C. (2022). Nurse licensure compact and mobility. \textit{Journal of Labor Research}. \hfill \href{https://www.dropbox.com/scl/fi/wfiwi8em9sbat5u9fcau2/Nurse-Licensure-Compact-and-Mobility.pdf?rlkey=8oved5beoz93zlxvhfzkzxx9i&dl=0}{Download}

\item \textbf{Shakya, S.}, \& Harrish, S. (2022). Medicaid expansion and opioid supply policies to address the opioid crisis. \textit{Drug and Alcohol Dependence Reports}. \hfill \href{https://www.dropbox.com/scl/fi/7m3j494m07g6dbt9ct1mt/Medicaid-expansion-and-opioid-supply-policies-to-address-the-opioid-overdose-crisis.pdf?rlkey=2s7ealv7uoxfikvteas8kbi3g&dl=0}{Download}

\item \textbf{Shakya, S.}, Li, B., \& Etienne, X. (2022). Shale revolution, oil and gas prices, and drilling activities in the United States. \textit{Energy Economics}. \hfill \href{https://www.dropbox.com/scl/fi/o0yruunqmgeig96pqmlag/Shale-Revolution-Oil-and-Gas-Prices-and-Drilling-Activities-in.pdf?rlkey=2fxzwf5jagb8nwrfnue414eqr&dl=0}{Download}

\item \textbf{Shakya, S.}, Plemmons, A., \& Sayago-Gomez, J. T. (2022). Spatial spillovers and the productivity-compensation gap in the United States. \textit{The Annals of Regional Science}. \hfill \href{https://www.dropbox.com/scl/fi/tf99i7zifoqrx9zyyybpj/Spatial-Spillovers-and-the-Productivity-Compensation.pdf?rlkey=kklhwmtat547j88dp7ghz4xwx&dl=0}{Download}

\item \textbf{Shakya, S.}, Basnet, S., \& Paudel, J. (2022). Natural disasters and labor migration: Evidence from Nepal's earthquake. \textit{World Development}. \hfill \href{https://www.dropbox.com/scl/fi/883lv35mzgnhdfnlmyeqt/Natural-disasters-and-labor-migration-Evidence-from-Nepal-s-earthquake.pdf?rlkey=8in4xafkl8su5e950dpn0uqrn&dl=0}{Download}

\item \textbf{Shakya, S.}, \& Plemmons, A. (2022). Productivity spillovers and the productivity-compensation gap. \textit{Spatial Economic Analysis}. \hfill \href{https://www.dropbox.com/scl/fi/0hspku758et24sw781ara/Shakya-Plemmons-SEA-2022.pdf?rlkey=y5ndrb1jilznbzzwfyxkmkdwa&dl=0}{Download}

\item Long, A. J., \textbf{Shakya, S.}, Plemmons, A., \& Stull, M. (2021). Is Time Really Money? Exploring the Temporal Actions Under Uncertainty in Crowdfunding Campaigns. \textit{Frontiers of Entrepreneurship Research}. \hfill \href{https://www.dropbox.com/scl/fi/0wr1vqkb980vtydusrp4t/ferpapers_4349.pdf?rlkey=il3xqgsy2502c1ywdifaj3ag6&st=ljdqj8xs&dl=0}{Download}

\item \textbf{Shakya, S.}, \& Sohag, K. (2021). The fracking boom and crime rates in the rural American states: Some critical insights. \textit{The Extractive Industries and Society}. \hfill \href{https://www.dropbox.com/scl/fi/sa9pq8amlw5hzhizqrt44/The-fracking-boom-and-crime-rates-in-rural-American-states-Some-critical-insights.pdf?rlkey=lo4r0ed4d3bo2gte4gctizy7d&dl=0}{Download}

\item \textbf{Shakya, S.}, \& Plemmons, A. (2021). The impact of economic freedom on startups. \textit{Journal of Regional Analysis and Policy}. \hfill \href{https://jrap.scholasticahq.com/article/18968-the-impact-of-economic-freedom-on-startups/attachment/50505.pdf}{Download}

\item \textbf{Shakya, S.}, Erfanian, E., \& Scarcioffolo, A. (2020). The political economy of Vermont's abortion bill. \textit{Applied Economics Letters}. \hfill \href{https://www.tandfonline.com/doi/abs/10.1080/13504851.2020.1854663}{Download}

\item \textbf{Shakya, S.}, \& Plemmons, A. (2020). Does scope of practice affect mobility of nurse practitioners serving Medicare beneficiaries? \textit{Journal of Labor Research}. \hfill \href{https://www.dropbox.com/scl/fi/va11jwf56xhnqmwdi985j/Does-Scope-of-Practice-Affect-Mobility-of-Nurse-Practitioners-Serving-Medicare-Beneficiaries.pdf?rlkey=htja0s8nr7ifete5a7jy5f3r4&dl=0}{Download}

\item Ismailova, Z., Etienne, X., \textbf{Shakya, S.}, \& Mattos, F. (2020). Quantifying the announcement effects in the US lumber futures market. \textit{Journal of Forest Economics}. \hfill \href{https://www.dropbox.com/scl/fi/guc5orscxfxccvng62u7n/Quantifying-The-Announcement-Effects-In-The-U.S.-Lumber-Market.pdf?rlkey=m26fvg1j27xxtrv4zyzcareck&dl=0}{Download}

\item Hall, J. C., Scarcioffolo, A. R., \& \textbf{Shakya, S.} (2020). The political economy of Vermont's anti-fracking movement. \textit{Journal of Public Finance and Public Choice}. \hfill \href{https://www.dropbox.com/scl/fi/xoxrp260dapkl450x60an/The-Political-Economy-of-Vermont-s-Anti-fracking.pdf?rlkey=vpf8i84sj0s3y4a66d3qsa8lb&dl=0}{Download}

\item \textbf{Shakya, S.} \& Sevigny, E. (2020). Replication of a research claim from Bersani and Doherty (2013). \textit{Center for Open Science, Systematizing Confidence in Open Research and Evidence (SCORE) Project}. \hfill \href{https://osf.io/9bme4}{Download}

\item Hall, J. \& \textbf{Shakya, S.} (2019). Federal regulations and US energy sector output. \textit{Oil, Gas, Energy Quarterly}, 68(2):229-241. \hfill \href{https://www.dropbox.com/scl/fi/evx1qev6p272vi87ogv3p/Federal-Regulations-and-U.S.-Energy-Sector-Output.pdf?rlkey=ewrftnbawujwqsaiqqvhko9m7&dl=0}{Download}

\item \textbf{Shakya, S.}, Nepal, R., \& Sharma, K. (2018). Electricity consumption and economic growth: empirical evidence from a resource-rich landlocked economy. \textit{International Journal of Global Energy Issues}, 41(5-6):226-247. \hfill \href{https://www.inderscience.com/offers.php?id=97139}{Download}

\item \textbf{Shakya, S.} \& Lama, N. (2016). Possible decision rules to allocate quotas and reservations to ensure equity for Nepalese poor. \textit{Economic Journal of Development Issues}, 17(1-2):149-162. \hfill \href{https://www.dropbox.com/scl/fi/bex13j7asy4007n51h3ex/11801.pdf?rlkey=56d65l8c3aw93ehwcw3z98f4c&dl=0}{Download}

\end{etaremune}

\section*{POLICY BRIEFS}
\begin{etaremune}
\item Plemmons, A., \textbf{Shakya, S.}, \& Timmons, E. (2024). Rural health care access in North Dakota: Unlocking the potential of health care providers. \textit{Sheila and Robert Challey Institute, North Dakota State University, Research Insights}. \hfill \href{https://www.ndsu.edu/fileadmin/challeyinstitute/Research_Briefs/Rural_Health_Care_Access.pdf}{Download}

\item \textbf{Shakya, S.} (2024). Understanding the role of immigrants in the US health sector: Employment trends from 2007-21. \textit{Rice University, Baker Institute for Public Policy, Center for the US and Mexico, Research Paper}. \hfill \href{https://www.bakerinstitute.org/research/understanding-role-immigrants-us-health-sector-employment-trends-2007-21}{Download}

\item \textbf{Shakya, S.}, Bae, K., Norris, C. and Timmons, E. (n.d.). Nurse Practitioner Full Practice Authority and Access to Primary Care in North Carolina. \hfill \href{https://csorwvu.com/np_full_practice_authority_nc/}{Download}

\item Bae, K., Norris, C., \textbf{Shakya, S.}, \& Timmons, E. (2022). Maryland's health care lesson for Pennsylvania: How full practice authority can increase access and improve outcomes. \textit{The Commonwealth Foundation}. \hfill \href{https://www.commonwealthfoundation.org/wp-content/uploads/2022/11/Expanding-Health-Care-Access.pdf}{Download}

\end{etaremune}

\section*{OP-EDS AND POPULAR WRITING}
\begin{etaremune}
\item Babaei-Balderlou, S., \& \textbf{Shakya, S.} (2026, March 5). We designed an AI tutor that helps college students reason rather than give them answers. \textit{The Conversation}. \hfill \href{https://theconversation.com/we-designed-an-ai-tutor-that-helps-college-students-reason-rather-than-give-them-answers-276584}{Link}
\end{etaremune}

\section*{BOOK CHAPTERS}
\begin{etaremune}
\item Pham, T., \textbf{Shakya, S.}, and Scarcioffolo, A. (2025). The Impact of Funded Campaigns in Shaping Voting Outcomes - A Case of California Proposition 8, \textit{Empirical Applications of the Median Voter Model}.

%\item \textbf{Shakya, S.}. (n.d.). Occupations, legislation, and licensing in Nepal. \textit{In International handbook of occupational licensing}.

\end{etaremune}


\section*{EXTERNAL FUNDING}
\begin{etaremune}
\item Flourishing and the Future Conference at Chetola Resort at Blowing Rock. \textbf{\$100,000} Funded. Aug 2025.
\item NIH AIM-AHEAD Program for Artificial Intelligence Readiness (PAIR) Program Cohort. \textbf{\$125,000} Not Funded. Jan 2025.
\item Long-Term Mental Health Impacts of Climate Change-Related Natural Disasters: A Causal Analysis of Depressive and Cognitive Symptoms, Research at Appalachian Impact Seed Funding (REALISE) program. \textbf{\$13,500} Not Funded. 2024.
\item \textbf{Shakya, S.} (2024). Understanding the role of immigrants in the US health sector: Employment trends from 2007-21. Center for the United States and Mexico, Rice University's Baker Institute for Public Policy. \textbf{\$3,500} Funded.
\item Ammons, J. and \textbf{Shakya, S.} (2024). Seeding reform or reaping chaos? Liberal institutional outcomes of violent vs. nonviolent revolutionary regime changes, Governing Deep Differences Grant Program, Center for Governance and Markets, University of Pittsburgh. \textbf{\$9,500} Funded.
\item Timmons, E., Bae, K., and \textbf{Shakya, S.} (2023). Nurse practitioner scope of practice and access to primary care in North Carolina, The John William Pope Foundation. \textbf{\$115,000} Funded.
\item Poghosyan, L. et al. (2023). Eliminating Policy Restrictions to Improve Access to Care and Economic Stability in Racial and Ethnic Minority Communities, National Institutes of Health, Transformative Research to Address Health Disparities and Advance Health Equity (U01 Clinical Trial Optional). \textbf{\$4,400,000} Not Funded.
\item Ghosh, S., Plemmons, A., and \textbf{Shakya, S.} (2023). Nurse Licensure Compacts and Public Health Emergencies. \textbf{\$150,000} Not Funded.
\item Ghosh, S., Plemmons, A., and \textbf{Shakya, S.} (2023). NCSBN Center for Regulatory Excellence. \textbf{\$15,000} Not Funded.
\item Bae, K., Norris, C., \textbf{Shakya, S.}, \& Timmons, E. (2022). Maryland's health care lesson for Pennsylvania: How full practice authority can increase access and improve outcomes. The Commonwealth Foundation. \textbf{\$15,000} Funded.
\end{etaremune}

\section*{INTERNAL GRANTS}
\begin{etaremune}
\item Sugg, M., Ulrich, S., Runkle, J., Tyson, J., and \textbf{Shakya, S.} (2024). Uncovering maternal healthcare deserts: A geospatial exploration of access disparities in the United States. University Research Council Grants, Appalachian State University. \textbf{\$4986} Funded.
\end{etaremune}

\section*{AWARDS}
\begin{list1}
\item[] Article of the Year, \textit{Journal of Rural Health} (National Rural Health Association) \hfill 2026
\item[] AIM-AHEAD Bridge2AI for Clinical Care Training Program - Cohort 1 Award \hfill 2025
\item[] Dean's Club Research Prize, Walker College of Business, Appalachian State University (Runner-up) \hfill 2024
\item[] Graduate Student-Authored Paper, The North American Regional Science Council (NARSC) Student Paper Competition Results  (1st Runner-up) \hfill 2019
\item[] Jon Vilasuso Advanced Doctoral Student Award, West Virginia University \hfill 2019
\end{list1}

\section*{DEPARTMENTAL SERVICES}
\begin{list1}
\item[] WCOB Artificial Intelligence Working Group \hfill Spring 2025
\item[] Dean's Club Research Prize committee, Walker College of Business \hfill Spring 2025
\item[] First Year Scholarship Review \hfill Fall 2024
\item[] Economics Faculty Search Committee \hfill Spring 2024 
\item[] Brashear Prize Selection Committee \hfill Fall 2023/24, Spring 2024/25
\item[] WCOB Curriculum Committee \hfill Fall 2024, Spring 2025
\end{list1}

\section*{DISCIPLINARY SERVICES}
\begin{list1}
\item[] \textbf{Editorial Manager}: Journal of Substance Use and Addiction Treatment \hfill 2024-Current
\item[] \textbf{Reviewer:} Journal of Comparative Economics (2026), Small Business Economics (2026), Health Affairs (2026), Journal of Economic Behavior and Organization (2025), Journal of Regulatory Economics (2025), Health Affairs (2025), Journal of Institutional Economics (2025), Small Business Economics (2025), Southern Economic Journal (2025), Contemporary Economic Policy (2025), Public Choice (2025), Journal of Regulatory Economics (2025), Southern Economic Journal (2024), Journal of Substance Use and Addiction Treatment (2024), Drug and Alcohol Review (2023), Energy Economics (2023), Pharmacoepidemiology and Drug Safety (2023), Small Business Economics (2023), Journal of Sports Economics (2023), Journal of Economic Geography (2023), Journal of Labor Research (2023), World Bank Economic Review (2022), Economic Modelling (2022), Drug and Alcohol Dependence (2022), Papers in Regional Science (2021), Journal of Regional Analysis and Policy (2021), Contemporary Economic Policy (2020), and PLOS One (2020).
\item[] \textbf{Chief Data Editor}: Journal of Comments and Replications in Economics \hfill 2022-2023
\item[] \textbf{Board of Directors}: Pennsylvania Economic Association \hfill 2022-2023
\item[] \textbf{Technical Editor}: Review of Regional Studies \hfill 2020-2022
\item[] \textbf{Data Editor}: Journal of Comments and Replications in Economics \hfill 2020-2022
\end{list1}

\section*{MEDIA COVERAGE}
\begin{etaremune}
\item Guest segment on an AI tutor that helps college students reason rather than give them answers. \textit{The Last Show with David Cooper} (Apple Podcasts), March 2026. \hfill \href{https://podcasts.apple.com/ca/podcast/full-episode-bell-bottoms-may-never-die-march-23-2026/id1168275879?i=1000756951575}{Link}

\item The Carolina Journal. (2025, January 14). Central planning fails in health care. \textit{The Carolina Journal}. Retrieved from \hfill \href{https://www.carolinajournal.com/opinion/central-planning-fails-in-health-care/}{Link}.

\item InForum. (2024, February 12). The right prescription for further improvement in North Dakota health care. \textit{InForum}. Retrieved from \hfill \href{https://www.inforum.com/opinion/letters/letter-the-right-prescription-for-further-improvement-in-north-dakota-health-care}{Link}.

\item ABC-7. (2024, January 8). FGCU professor says public libraries lower crime. \textit{ABC-7}. Retrieved from \hfill \href{https://www.abc-7.com/article/fgcu-professor-says-public-libraries-lower-crime/46689106}{Link}.

\item News-Medical. (2024, January 8). Immigrant healthcare professionals: essential pillars of the U.S. health system. \textit{News-Medical}. Retrieved from \hfill \href{https://www.news-medical.net/news/20240108/Immigrant-healthcare-professionals-essential-pillars-of-the-US-health-system.aspx}{Link}.

\item WisPolitics. (2023, November 14). Wisconsin is right to reimagine nurse practitioners to address healthcare shortages. \textit{WisPolitics}. Retrieved from \hfill \href{https://www.wispolitics.com/2023/alicia-plemmons-wisconsin-is-right-to-reimagine-nurse-practitioners-to-address-healthcare-shortages/}{Link}.

\item Frontier Institute. (2023, May 16). Reforms to increase Montanans access to healthcare are a welcome development, let's hope lawmakers agree. \textit{Frontier Institute}. Retrieved from \hfill \href{https://frontierinstitute.org/the-reform-to-expand-access-to-healthcare-in-rural-montana/}{Link}.

\item Deseret News Editorial Board. (2023, May 16). Pharmacists and psychologists prescribing medication: A new law. \textit{Deseret News}. Retrieved from \hfill \href{https://www.deseret.com/opinion/2023/5/16/23721625/pharmacists-psychologists-prescribe-medication-law}{Link}.

\item Missoulian Opinion, (2023, March 16). Montana can become a national leader by empowering pharmacists. \textit{Missoulian}. Retrieved from \hfill \href{https://missoulian.com/opinion/column/alicia-plemmons-montana-can-become-a-national-leader-by-empowering-pharmacists/article_2195cdb4-bdec-11ed-bb42-4b2d76a0b8cf.html}{Link}.

\item Modern Healthcare. (2023, March 2). Pharmacists know all about medications, so why can’t they prescribe them?. \textit{Modern Healthcare}. Retrieved from \hfill \href{https://www.modernhealthcare.com/opinion/pharmacists-prescribing-authority-alicia-plemmons-west-virginia-university}{Link}.
\end{etaremune}

\section*{INVITED RESEARCH PRESENTATION}
\begin{etaremune}
\item \textbf{Shakya, S.} (2026). State-level policies and healthcare. Human Progress and Flourishing Workshop, Sheila and Robert Challey Institute for Global Innovation and Growth, North Dakota State University, Fargo, ND, April 10, 2026. \hfill \href{https://www.ndsu.edu/challeyinstitute/events/workshop}{Link}

\item From License to Practice: Gender Disparities in Health Care. Appalachian State University, April 2025.

\item Bailey, J., \& \textbf{Shakya, S.} (n.d.). The impact of repealing Certificate-of-Need laws on healthcare spending: A causal analysis. Research and Creative Activity at Appalachian, Appalachian State University, February 2025.

\item \textbf{Shakya, S.}, Ammons, J., and Geloso, V. (n.d.). The polyarchy paradigm: Unraveling corruption and fostering transparency, Stephenson Institute, Washington DC, November 2024.

\item \textbf{Shakya, S.}, Ammons, J., Mahmood, T. I. (n.d.). How Do Revolutions Affect Development?, Stephenson Institute, Washington DC, November 2024.

\item Ammons, J., \textbf{Shakya, S.}, \& Callais, J. T. (n.d.). What do women get from a successful revolution? Journal of Institutional Economics (JOIE) Symposium Research Workshop, Washington DC, October 2024.

\item \textbf{Shakya, S.}, \& Plemmons, A. (n.d.). Regional institutional quality and job creation among early startups in the United States. Menard Family Initiative Entrepreneurship Conference at University of Wisconsin-La Crosse, October 2024.

\item Regulation and health - Wins for everyday citizens (summaries of my works on various state policies). The Classical Liberals in the Carolinas, August 2024.

\item Advancing healthcare access: State policy innovations and evidence-based research (summaries of my works on various state policies). The Appalachian Institute to Advance Health Equity Science (ADVANCE), Ohio University, April 2024.

\item Basics of causal inference. Nepali Academics in America, March 2024.

\item Advanced causal inference. Andrew Young School of Policy Studies, Georgia State University, March 2024.

\item \textbf{Shakya, S.}, Bedi, J., \& Plemmons, A. (n.d.). Healthcare workforce shortages and job autonomy: Nurse practitioners and entrepreneurship in the United States. SJSU Philosophy, Politics, and Economics Research Seminar, San Jose State University, March 2024.

\item \textbf{Shakya, S.}, \& Roy, A. (n.d.). Access to mental health care services and suicide rates in the United States. Darla Moore School of Business, University of South Carolina, October 2023.

\item \textbf{Shakya, S.}, \& Bretschneider Fries, C. (2024). The effect of substance use Certificate-of-Need laws on access to substance use disorder treatment facilities. \textit{Southern Economic Journal}. Towson University, September 2023.

\item \textbf{Shakya, S.} (2024). Understanding the role of immigrants in the US health sector: Employment trends from 2007-21. Immigration Impacts on Healthcare, Institute for Humane Studies, September 2023.

\item \textbf{Shakya, S.}, \& Roy, A. (n.d.). Access to mental health care services and suicide rates in the United States. Liberty over Lunch Seminar, Western Carolina University, September 2023.

\item \textbf{Shakya, S.}, \& Plemmons, A. (n.d.). Scope of practice and opioid prescribing behavior of nurse practitioners serving Medicare beneficiaries. Towson University, September 2022.

\item \textbf{Shakya, S.} (n.d.). Impact of must-access PDMPs on prescription opioid overdose death rates. Investigation of Healthcare Regulation Workshop: The Institute for Humane Studies, July 2022.

\item \textbf{Shakya, S.}, \& Plemmons, A. (n.d.). Scope of practice and opioid prescribing behavior of nurse practitioners serving Medicare beneficiaries. The 36$^{th}$ Annual Conference of Pennsylvania Economic Association, June 2022.

\item Economics of investment and personal finance. Economics of Personal Investing, Investment Club Shippensburg University, March 2022.

\item Shah Mobariz, A., \& \textbf{Shakya, S.} (2024). Cultural influences on gender gap in test scores: Findings from Afghanistan's university entrance examination. Dickinson College, March 2022.

\item \textbf{Shakya, S.}, Basnet, S., \& Paudel, J. (2022). Natural disasters and labor migration: Evidence from Nepal's earthquake. Institute for Integrated Development Studies (IIDS), March 2022.

\item Labor market effects of the scope of practice policies. The Institute for Humane Studies and Arkansas Center for Research in Economics, January 2022.

\item \textbf{Shakya, S.}, \& Levinstein, M. (2024). Grading policy, email nudges, and grade outcomes. Pennsylvania's State System of Higher Education (PASSHE) Conference on Teaching and Learning, January 2022.

\item \textbf{Shakya, S.}, \& Plemmons, A. (n.d.). Scope of practice and opioid prescribing behavior of nurse practitioners serving Medicare beneficiaries. Gulati Institute of Finance and Taxation, November 2021.

\item \textbf{Shakya, S.}, \& Levinstein, M. (2024). Grading policy, email nudges, and grade outcomes. Center for Social Research, November 2021.

\item \textbf{Shakya, S.}, Ghosh, S., \& Norris, C. (2022). Nurse licensure compact and mobility. National Council of State Boards of Nursing (NCSBN), September 2021.

\item \textbf{Shakya, S.}, \& Plemmons, A. (2020). Does scope of practice affect mobility of nurse practitioners serving Medicare beneficiaries? The Arkansas Center for Research in Economics (ACRE), October 2020.

\item Causal inference workshop. Economics Students' Society Nepal, September 2020.

\item \textbf{Shakya, S.} (n.d.). Heterogeneous Treatment Effects of Medicaid and Efficient Policies. Icesi University, May 2020.
\end{etaremune}

\section*{CONFERENCE PRESENTATIONS}
\begin{etaremune}
\itemsep0em
\item[] Multiple papers presentation, discussants of multiple papers, and session chairs.
\item Flourishing and the Future Conference, Boone, NC \hfill Aug 2025
\item 2025 AIM-AHEAD Annual Meeting, Fort Worth, TX \hfill Jul 2025
\item Bridge2AI All Hands Conference, Rockville, MD \hfill May 2025
\item Association of Private Enterprise Education (APEE), Guatemala \hfill Apr 2025
\item Public Choice Society Annual Meetings, Louisville, KY  \hfill Mar 2025
\item Southern Economic Association (SEA), Washington, DC \hfill Nov 2024
\item Annual Global Symposium, Boone, NC \hfill Nov 2024
\item 2024 Markets and Society Conference, Washington, DC \hfill Oct 2024
\item Research and Creative Activity at Appalachian, Boone, NC \hfill Sep 2024
\item The Classical Liberals in the Carolinas, Greenville, SC \hfill Aug 2024
\item The Classical Liberals in the Carolinas, Winston-Salem, NC \hfill Aug 2024
\item Scope of Practice Conference, West Virginia University, Morgantown, WV \hfill Jul 2024
\item Advancing Health Equity in Rural Communities, Boone, NC \hfill May 2024
\item Appalachian Experimental and Environmental Economics Workshop, Boone, NC \hfill Apr 2024
\item The Association of Private Enterprise Education: APEE, Las Vegas, NV \hfill Apr 2024
\item Southern Economic Association (SEA), New Orleans, LA \hfill Nov 2023
\item Carolina Region Empirical Economics Day (CREED) Program, Columbia, SC \hfill Oct 2023
\item 1st Certificate of Need Law Research Conference, Morgantown, WV \hfill Jun 2023
\item Southern Economic Association (SEA), Fort Lauderdale, FL \hfill Nov 2022
\item ASHEcon -- American Society of Health Economists, Austin, TX \hfill Jun 2022
\item The Association of Private Enterprise Education (APEE), Las Vegas, NV  \hfill Apr 2022
\item AEA Annual Meeting \hfill Jan 2022
\item Southern Economic Association (SEA), Houston, TX \hfill Nov 2021
\item ASHEcon -- American Society of Health Economists, Virtual \hfill Jun 2021
\item Western Economic Association International, Virtual \hfill Jun 2021
\item Knee Center Occupational Licensing Conference, West Virginia University, Virtual \hfill May 2021
\item The Southern Regional Science Association (SRSA), Virtual \hfill Mar 2021
\item Southern Economic Association (SEA), Virtual \hfill Nov 2020
\item The North American Regional Science Council (NARSC), Virtual \hfill Nov 2020
\item Symposium on Data Science and Statistics, Virtual \hfill Jun 2020
\item Annual Knee Center Occupational Licensing Conference, Virtual \hfill May 2020
\item The Southern Regional Science Association (SRSA), Washington, DC \hfill 2019
\item The North American Regional Science Council (NARSC), Pittsburgh, PA \hfill 2019
\item Public Choice Society Annual Meetings, Louisville, KY \hfill 2019
\item Graduate Research Workshop - Institute for Humane Studies, Washington, DC \hfill 2019
\item YSI North America Convening, Los Angeles, CA \hfill 2019
\item The Southern Regional Science Association (SRSA), Philadelphia, PA \hfill 2018
\item The North American Regional Science Council (NARSC), San Antonio, TX \hfill 2018
\item Applied Economics and Regional Science (AERS), Columbus, OH \hfill 2018
\item The Southern Regional Science Association (SRSA), Memphis, TN \hfill 2017
\item Applied Economics and Regional Science (AERS), Morgantown, WV \hfill 2017
\end{etaremune}

\section*{MENTORSHIP}
\begin{list1}
\item[] Indira Kuppa, Master's Student, Healthcare Informatics, George Mason University \hfill 2025
\item[] Dharmi Kalpesh Desai, Health Services Research, Department of Economics, George Mason University \hfill 2025
\item[] Jake Sheeler, MBA, Walker College of Business, Appalachian State University \hfill 2024
\item[] Anna Carroll, BSBA, Walker College of Business, Appalachian State University \hfill 2024
\item[] Salpy Kanimian, Ph.D. Candidate, Department of Economics, Rice University \hfill 2024
\item[] Mukesh Adhikari, Ph.D. student, University of North Carolina, Gillings School of Global Public Health, Department of Health Policy and Management \hfill 2024
\item[] Edgar Orozco, Ph.D. Candidate, Department of Economics, West Virginia University \hfill 2024
\item[] Tulasi Ram Nepal, Ph.D. student, Fogelman College of Business and Economics, The University of Memphis. \hfill 2023
\item[] Sukriti Beniwal, Ph.D. Candidate, Department of Economics, Georgia State University \hfill 2024
\item[] Christine Bretschneider Fries, Department of Economics, West Virginia University \hfill 2023
\item[] Joshua D. Ammons, Ph.D. Candidate, Department of Economics, George Mason University \hfill 2023-Current
\end{list1}


\bigskip 
\begin{center}
 \begin{footnotesize}
 Last updated: \today \\
 \href{\footerlink}{\texttt{\footerlink}}
 \end{footnotesize}
\end{center}